---
title: "ESM206 Lab 10"
author: "Karina Johnston"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Attach packages
library(tidyverse)
library(janitor)

# Attach new packages
library(usethis)
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```


## Use `beepr::beep()`

Good for sounds for when code is done running - good if you have a long complicated code that you need to know when its done running.

```{r}
beep(8)
```

## For loop, using `beep()` when done

Write a for loop

```{r, eval = FALSE}
# 99 bottles of beer on the wall...

for(i in rev(seq(1:999))) {
  print(paste(i, "bottles of beer on the wall..."))
}

beep(4)

```

## Using `praise()`

Nice messages only!
can specify template for grammatical look of it

```{r}
# specify template pieces

praise("${EXCLAMATION}!!! This code works ${adverb_manner}!")

```

## Using the cowsay package

only has a single function `cowsay::say()`

```{r}
say("I love Karina!", by = "shark")
```

## Usethis for everything

Allison's favorite r package
can make your life easier!

`usethis::edit_r_profile()`

```{r}
# updating R profile - settings associated with your default R sessions

```

R Project first, then create a github

`usethis:use_git()`
then `usethis::use_github()`

do it in your console

## Use Palatteer package

new color palettes!


```{r}
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  slice_min(n = 10, min_pressure) %>% 
  ggplot(aes(x = min_pressure,
             y = name)) +
  geom_col(aes(fill = name)) +
  theme_classic() +
  scale_fill_paletteer_d("colorBlindness::Blue2Orange10Steps")

# basetheme::deepblue
# ggprism::colors
```

## Make a map!!

Of the Jornada LTER vegetation
use the sf package

```{r}
# read in the .kml file

jornada_veg <- read_sf("doc.kml")
```

```{r}
jornada_veg %>% 
  select(Name) %>% 
  clean_names() 

```

create plot, update theme, veg color, and palette

```{r}
ggplot() +
  geom_sf(data = jornada_veg, aes(fill = Name), color = NA) +
  theme_classic() +
  scale_fill_paletteer_d("ggthemes::manyeys")


```



